Assessing Factors Affecting Student's Performance during COVID-19 Pandemic

### 2024-02-15 outputs/paper/paper.qmd
Final

---
title: "Assessing Factors Affecting Student's Performance during COVID-19 Pandemic"
subtitle: "Data from USA"
author: 
  - Vanshika Vanshika 
  - Shivank Goyal
  - Navya Hooda
thanks: "Code and data are available at: https://github.com/shivankgoel003/Student-Performance-COVID-19-US-States-Factors; Minimal and Full Replication on Social Science Reproduction platform available at [https://www.socialsciencereproduction.org/reproductions/1470/published/index](https://www.socialsciencereproduction.org/reproductions/1470/published/index) "
date: today
date-format: long
abstract: "We analyze data from 11 U.S. states to assess the correlation between factors that may be indicative of student performance during COVID-19 learning disruptions. This paper replicates data analysis upon pandemic schooling and its affect on student test scores, and  further attempts to understand other mechanisms that led to learning losses during this period. Several charesteritics were related to student performance: mode of learning, loss of COVID-19 case rates, employment and student-to-staff ratio.The learning losses were found to be around 13–14 percentage points in math and approximately 8 percentage points in ELA between 2019 and 2021 (Jack and Oster 2023). In particular we discover that  all factors except student-to-staff ratio were relevant predictors and contributed to noticeable differences when compared to 2019 (pre-covid), these findings suggest that the factors that normally contribute to student performance had exacerbated effects during COVID-19 as they led to a larger magnitude of learning losses."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

>>>>

---
title: "Assessing Factors Affecting Student's Performance during COVID-19 Pandemic"
subtitle: "Data from USA"
author: 
  - Vanshika Vanshika 
  - Shivank Goel
  - Navya Hooda
thanks: "Code and data are available at: https://github.com/shivankgoel003/Student-Performance-COVID-19-US-States-Factors; Minimal and Full Replication on Social Science Reproduction platform available at [https://www.socialsciencereproduction.org/reproductions/1470/published/index](https://www.socialsciencereproduction.org/reproductions/1470/published/index) "
date: today
date-format: long
abstract: "We analyze data from 11 U.S. states to assess the correlation between factors that may be indicative of student performance during COVID-19 learning disruptions. This paper replicates data analysis upon pandemic schooling and its affect on student test scores, and  further attempts to understand other mechanisms that led to learning losses during this period. Several charesteritics were related to student performance: mode of learning, loss of COVID-19 case rates, employment and student-to-staff ratio.The learning losses were found to be around 13–14 percentage points in math and approximately 8 percentage points in ELA between 2019 and 2021 (Jack and Oster 2023). In particular we discover that  all factors except student-to-staff ratio were relevant predictors and contributed to noticeable differences when compared to 2019 (pre-covid), these findings suggest that the factors that normally contribute to student performance had exacerbated effects during COVID-19 as they led to a larger magnitude of learning losses."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---
